Arc Blanc: a real time ocean simulation framework

### 2025-01-10 paper.tex
Add a missing word
Remove the +1 to avoid confusion

This distribution is designed based on the following considerations.
First, while the velocity decays exponentially, it relies on a logarithmic similar to $y_i\mapsto \ln(|y_i|+1)$.
Since this function transforms the negative $y_i$ into a positive one, the result is multiplied by the sign of $y_i$.
Also, this function decreases slowly (actually with $\ln(250+1)=5.5$), hence the logarithmic distribution uses the square of $|y_1|$.
Lastly, the parameter $\alpha$ controls the “squeezing” in the center, while the parameter $\beta$ controls the deepest value of $l_d$.
Notice that $\beta$ is chosen as the solution of $l_d(y_{min})=\frac{y_{min}}{2}$ but not at $y_{min}$: it is the solution giving the best accuracy after multiple tries.

>>>>

This distribution is designed based on the following considerations.
First, while the velocity decays exponentially, it relies on a logarithmic function similar to $y_i\mapsto \ln(|y_i|+1)$.
Since this function transforms the negative $y_i$ into a positive one, the result is multiplied by the sign of $y_i$.
Also, this function decreases slowly (actually with $\ln(250)=5.5$), hence the logarithmic distribution uses the square of $|y_1|$.
Lastly, the parameter $\alpha$ controls the “squeezing” in the center, while the parameter $\beta$ controls the deepest value of $l_d$.
Notice that $\beta$ is chosen as the solution of $l_d(y_{min})=\frac{y_{min}}{2}$ but not at $y_{min}$: it is the solution giving the best accuracy after multiple tries.
